### 2016-06-07 Standardmodel.tex
TreeLevel CrossSection and SM-Introduction

\section{The Standard Model}
The Standard Model of particle physics is the commonly accepted theory describing the world's fundamental particles and their interactions. It is a gauge quantum field theory which is characterized by its invariance under different symmetry groups. The Standard Model contains different fields, whose quantized excitations are interpreted as particles.\\
%The different fields defined on Minkowski space are Dirac spinors describing matter fields (leptons and quarks), gauge vectors describing force mediators and a scalar field (the Higgs) which accounts for the masses of particles.\\
%More formally a particle state is said to give rise to an irreducible representation of the Poincaré group

\subsection{Symmetries and Transformations}
\subsubsection*{Spacetime Symmetries}
The Standard Model is defined on Minkowski space, whose coordinates are label with $x^\mu$ $\mu = \left\{0,1,2,4\right\}$. As a relativistic theory it is invariant under Poincaré transformations, i.e. it is invariant under Lorentz-transformations (with generators $J^{\mu\nu}$) and translations (with generators $P^\mu$) in spacetime. The set of all Poincaré transformations form the Poincaré group, which is a Lie group. Its generators obey the Poincaré-algebra
\begin{align}
[P^\mu,P^\nu] &= 0\nonumber\\
[P^\mu,J^{\nu\rho}] &= i(g^{\mu\nu} P^\rho - g^{\mu\rho}P^\nu)\nonumber\\
[J^{\mu\nu},J^{\rho\sigma}] &= i(g^{\nu\rho}J^{\mu\rho} + g^{\mu\sigma}J^{\nu\rho} - g^{\mu\rho}J^{\nu\sigma} - g^{\nu\sigma}J^{\mu\rho}).
\end{align}
The fields of the Standard Model transform in different representations of the Poincaré-group \cite{book:17018}.

@@

In order to describe interactions of matter particles one uses gauge theories. In the Standard Model matter fields are described by Dirac spinors. The Lagrangian of a free Dirac field reads

@@

Because the parameters of the gauge group are local the derivative in \ref{eq:DiracLagrangian} spoils the gauge invariance. In order to rectify gauge invariance of the Lagrangian one can introduce a further field for each index $a$ of the generators - the gauge vector $G^{a\mu}$. Defining the transformation of the matrix valued gauge vector $G^\mu := G^{a\mu}T^a$ as 

@@

G^{\mu}(x) \to U(x) \left( G^\mu(x) + \frac{i}{g}\partial^\mu \right) U^{-1}(x)

@@

Therefore gauge invariance in \ref{eq:DiracLagrangian} is restored by replacing $\partial_\mu$ with $D_\mu$. But if the gauge vector is interpreted as a physical field there must apart from the so far introduced interaction term also be a kinetic term associated with it. Using \ref{eq:CovDerivative} one defines the field strength tensor\footnote{An alternative construction makes use of the gauge invariant Wilson loop. This gives some insights into the geometry of gauge transformations \cite{Peskin}.} $F^{a\mu\nu}$ whose matrix valued form

@@

F^{\mu\nu} = F^{a\mu\nu}T^a = \frac{1}{ig}[D^\mu,D^\nu] = \partial^\mu G^\nu - \partial^\nu G^\mu - i f_{abc}....

@@

transforms as $F^{\mu\nu} \to U(x)F^{\mu\nu}U^{-1}(x)$. Using the cyclic property of the trace and the Dynkin index $T(F)$ defined in the appendix \ref{eq:DynkinIndex}  one can write down a gauge invariant kinetic term for the gauge vector:

@@

This completes the construction of a Lagrangian which is invariant under non-abelian gauge group transformations. The result is the famous Yang and Mills Lagrangian[cite original paper]

@@

This Lagragian gives rise to spin-$\frac{1}{2}$ (matter) particles which interact with spin-1 (force mediator) particles with each other. Furthermore if the gauge group is non-abelian, i.e. $f_{abc} \neq 0$, there are self interactions among the spin-1 particles.\\
The gauge group of the SM is a direct product ??? of the three gauge groups: $U_Y(1)$, $SU_L(2)$ and $SU_C(3)$\footnote{The subscript stands for the associated charge of the groups respectively: $Y$ for hypercharge, $L$ for left handedness (weak Isospin $I_3$) and $C$ for color}. The elements $U(x)$ of those and the infinitesimal transformations of the spinors and gauge vectors are given in table \ref{tab:SM_transformations}.\\

@@

\begin{tabular}{|c|l|}

@@

 & $U(x) = \mathrm{exp}\left(-ig_Y\frac{\hat{Y}}{2}\theta_Y(x)\right)$\\
 $U_Y(1)$ & $\psi(x) \to \left( 1 - ig_Y\frac{\hat{Y}}{2}\theta_Y(x)\right)\psi(x)$\\
 & $B^\mu(x) \to B^\mu(x) + \partial^\mu\theta_Y(x)$\\

@@

 & $U(x) = \mathrm{exp}\left(-ig_w \vec{\tau} \cdot \vec{\theta}_w(x)\right)$\\
 $SU_L(2)$ & $\psi(x) \to \left( \mathbbm{1} - ig_w \vec{\tau} \cdot \vec{\theta}_w(x)\right)\psi(x)$\\
 & $W^{a\mu}(x) \to W^{a\mu}(x) +\partial^\mu\theta^a_w(x) + g_w \varepsilon^{abc} \theta^b_w(x)W^{c\mu}(x)$\\
 & $U(x) = \mathrm{exp}\left(-ig_s T^a \cdot \theta_s^a(x)\right)$\\
$SU_C(3)$ & $\psi(x) \to \left(\mathbbm{1}-ig_s T^a \cdot \theta_s^a(x)\right)$\\
 & $G^{a\mu}(x) \to G^{a\mu}(x) + \partial^\mu\theta^a_s(x) + g_s f_{abc} \theta^b_s(x)G^{c\mu}$\\

@@

\caption{The table lists the explicit element $U(x)$ of the gauge groups $U_Y(1)$, $SU_L(2)$ and $SU_C(3)$ and the infinitesimal transformations of spinor and vector fields.\newline
The hypercharge operator $\hat{Y}$ gives the eigenvalue of the hypercharge of the field it is applied to. $\vec{\tau}$ and $T^a$ are the geneators of $SU_L(2)$ and $SU_C(3)$ respectively. In the fundamental representation one has $\vec{\tau} = \frac{\vec{\sigma}}{2}$ where $\vec{\sigma}$ has the 3 Pauli matrices as components and $T^a = \frac{\lambda^a}{2}$ where $\lambda^a$ are the 8 Gell-Mann matrices. $\varepsilon_{abc}$ and $f_{abc}$ are the structure constants of $SU_L(2)$ and $SU_C(3)$ respectively.}\label{tab:SM_transformations}

@@

@@

\newpage

@@

Furthermore the left handed component of quarks interact weakly, which means that their spinors transform (in the fundamental representation) under $SU_L(2)$ meaning that 2 left handed quark spinors are assembled in a doublet.\\
Finally all quarks carry a hypercharge. In section ??? the mechanism of electroweak symmetry breaking is described. This mechanism explains how electromagnetism arises from the groups $SU_L(2)$ and $U_Y(1)$. All quarks interact electromagnetically.\\
After all there are 6 quarks which are listed in table\ref{tab:generations}. They are categorized in 3 generations because their quantum numbers except (for their mass) is the same in each generation. The two types of quarks which have distinct quantum numbers are the up-type-quarks and the down-type quarks. A up-type-quark and the down-type quark of the same generation built up a doublet.

@@

\bigbreak
Quarks and Leptons are the matter particles of the SM. They are listed together with their charges for the different forces in table \ref{tab:SMfieldcontent}. One has the color for strong interactions, the third component of the weak isospin $I_3$ for weak interactions(the eigenvalue of the third generator of the $SU_L(2)$) and the half of the hypercharge $\frac{Y}{2}$ to obtain the electric charge $Q$ via the Gell-Mann–Nishijima formula: $Q = I_3 + \frac{Y}{2}$.\\
Because the left and right-handed parts of spinors transform differently under the $SU_L(2)$ they are listed separately.\\
All quarks occur with three different colors.\\

@@

@@

\caption{This table lists all matter particles in the SM and the Higgs particle with their charges for all forces. This is the color, the weak isospin $I_3$, the half of their hypercharge and their electrical charge. The index $i = 1,2,3$ labels the generation of the matter particles and is written out in table \ref{tab:generations}}\label{tab:SMfieldcontent}

@@

\subsubsection*{The Force Particles}
The force particles are described by gauge fields. The gluon field is the gauge field of $SU_C(3)$. Because the $SU_C(3)$ has 8 generators there are 8 gluons. Their coupling constant is $g_s$.\\
For the other force particles in the SM - the $W^\pm$ bosons, the $Z_0$ boson and the photon the is situation is slightly more involved. They are obtained as a mixture of the $W^b_\mu$ ($b=1,2,3$)and the $B_\mu$ field. This mixing procedure is referred to as electroweak symmetry breaking and is explained in section???.\\
For the moment being the coupling constants and gauge fields before and after EWSB are quoted in table \ref{tab:force_particles}
\begin{tabular}{c|c|c?c|c|c}
\multicolumn{3}{c?}{before EWSB} & \multicolumn{3}{c}{after EWSB}\\
group & coupling constant & gauge field & coupling constant & gauge field & Particle\\
$SU_C(3)$ & $g_s$ & $G^a_\mu$ & $g_s$ & $G^a_\mu$ & Gluon\\
$SU_L(2)$ & $g_w$ & $W^b_\mu$ & $g_W = \sqrt{2}g_w$,  &  $W^\pm_\mu$,  & $W^\pm$,  \\
 & & & $g_Z = \sqrt{g_w^2 + g_Y^2}$ & $Z^0_\mu$ & $Z^0$ Boson\\
$U_Y(1)$ & $g_Y$ & $B_\mu$ & $e = g_Y\cdot c_w$ & $A_\mu$ & Photon
\caption{The gauge fields and their coupling constants before and after EWSB. The Gluon field is not affected by EWSB. $a = 1,\hdots 8$ and $b=1,2,3$ label the number of gauge fields. $c_w$ is the cosine of the electroweak mixing angle defined in \ref{sec:EWSB}}\label{tab:force_particles}
The Lagrangian of the SM is built up by qualitatively different terms. Firstly there are the kinetic and minimal coupling terms of the matter fields 
\mathcal{L}_{matter} =  \sum_{i=1}^3 \left( \overline{\ell}_{iL} i \slashed{D} l_{iL} + \overline{e}_{iR} i \slashed{D} e_{iR} + \overline{q}_{iL} i \slashed{D} q_{iL} + \overline{u}_{iR} i \slashed{D} u_{iR} \right)
where $i=1,2,3$ labels the generations of matter. The gauge covariant derivative is given by
D_\mu = \partial_\mu + i g_Y\frac{\hat{Y}}{2} +ig_w \vec{\tau}\cdot \vec{W}^\mu + i g_s T^a G_a^\mu
where for each field the corresponding representation (fundamental or trivial) of the gauge group is to be inserted (see table \ref{tab:SMfieldcontent}). The hyper charge operator $\hat{Y}$ gives the eigenvalue of the hypercharge of the field it is applied to. These can be found in table \ref{tab:SMfieldcontent}.
The kinetic terms of the gauge fields are given by
\mathcal{L}_{gauge} = -\frac{1}{4}F^{\mu\nu}F_{\mu\nu} - \frac{1}{4}W^{a\mu\nu}W^a_{\mu\nu} - \frac{1}{4}G^{a\mu\nu}G^a_{\mu\nu}

>>>>

\section{The Standard Model}
The Standard Model of particle physics is the commonly accepted theory describing the world's fundamental particles and their interactions. It is a gauge quantum field theory which is characterized by its invariance under symmetry groups. The Standard Model contains different fields, whose quantized excitations are interpreted as particles.\\
This chapter summarizes the most important aspects of the Standard Model.
%The different fields defined on Minkowski space are Dirac spinors describing matter fields (leptons and quarks), gauge vectors describing force mediators and a scalar field (the Higgs) which accounts for the masses of particles.\\
%More formally a particle state is said to give rise to an irreducible representation of the Poincaré group

\subsection{Symmetries and Transformations}
\subsubsection*{Spacetime Symmetries}
The Standard Model is defined on Minkowski space, whose coordinates are label with $x^\mu$ $\mu \in \left\{0,1,2,4\right\}$. As a relativistic theory it is invariant under Poincaré transformations, i.e. it is invariant under Lorentz-transformations (with generators $J^{\mu\nu}$) and translations (with generators $P^\mu$) in spacetime. The set of all Poincaré transformations form the Poincaré group, which is a Lie group. Its generators obey the Poincaré-algebra
\begin{align}
[P^\mu,P^\nu] &= 0\nonumber\\
[P^\mu,J^{\nu\rho}] &= i(g^{\mu\nu} P^\rho - g^{\mu\rho}P^\nu)\nonumber\\
[J^{\mu\nu},J^{\rho\sigma}] &= i(g^{\nu\rho}J^{\mu\rho} + g^{\mu\sigma}J^{\nu\rho} - g^{\mu\rho}J^{\nu\sigma} - g^{\nu\sigma}J^{\mu\rho}).
\end{align}
The fields of the Standard Model transform in different representations of the Poincaré-group \cite{book:17018}.

@@

In order to describe interactions of matter particles gauge theories are used. In the Standard Model matter fields are described by Dirac spinors. The Lagrangian of a free Dirac field reads

@@

Because the parameters of the gauge group are local the derivative in \ref{eq:DiracLagrangian} spoils the gauge invariance. In order to rectify gauge invariance of the Lagrangian one introduces a further field for each index $a$ of the generators - the gauge vector $G^{a\mu}$. Defining the transformation of the matrix valued gauge vector $G^\mu := G^{a\mu}T^a$ as 

@@

G^{\mu}(x) \to U^{-1}(x) \left( G^\mu(x) + \frac{i}{g}\partial^\mu \right) U(x)

@@

Therefore gauge invariance is restored in eq. \ref{eq:DiracLagrangian} by replacing $\partial_\mu$ with $D_\mu$. But if the gauge vector is interpreted as a physical field there must apart from the so far introduced interaction term also be a kinetic term associated with it. Using eq. \ref{eq:CovDerivative} one defines the field strength tensor\footnote{An alternative construction of the field strength tensor makes use of the gauge invariant Wilson loop. This gives some insights into the geometry of gauge transformations \cite{Peskin}.} $F^{a\mu\nu}$ whose matrix valued form

@@

F^{\mu\nu} = F^{a\mu\nu}T^a := \frac{1}{ig}[D^\mu,D^\nu] = \partial^\mu G^\nu - \partial^\nu G^\mu - g f_{abc} T^c G^{a\mu}G^{b\nu}

@@

transforms as $F^{\mu\nu} \to U(x)F^{\mu\nu}U^{-1}(x)$. Using the cyclic property of the trace and the Dynkin index $T(F)$ defined in eq. \ref{eq:DynkinIndex} in the appendix one can write down a gauge invariant kinetic term for the gauge vector:

@@

This completes the construction of a Lagrangian which is invariant under non-abelian gauge group transformations. The result is the famous Yang and Mills Lagrangian \cite{PhysRev.96.191}

@@

This Lagragian gives rise to spin-$\frac{1}{2}$ (matter) particles which interact with spin-1 (force mediator) particles. Furthermore if the gauge group is non-abelian, i.e. $f_{abc} \neq 0$, there are self interactions among the spin-1 particles.\\
The gauge group of the Standard Model is a direct product of the three gauge groups\footnote{The subscript stands for the associated charge of the groups respectively: $Y$ for hypercharge, $L$ for left handedness (weak Isospin $I_3$) and $C$ for color}: $U_Y(1)$, $SU_L(2)$ and $SU_C(3)$. The elements $U(x)$ of those are given in table \ref{tab:SM_transformations}.\\

@@

\begin{tabular}{c?c}
Gauge Group & Group Element\\
$U_Y(1)$ & $U(x) = \mathrm{exp}\left(-ig_Y\frac{\hat{Y}}{2}\theta_Y(x)\right)$\\

@@

$SU_L(2)$ & $U(x) = \mathrm{exp}\left(-ig_w \vec{\tau} \cdot \vec{\theta}_w(x)\right)$\\

@@

$SU_C(3)$ & $U(x) = \mathrm{exp}\left(-ig_s T^a \cdot \theta_s^a(x)\right)$

@@

\caption{The table lists the explicit element $U(x)$ of the gauge groups $U_Y(1)$, $SU_L(2)$ and $SU_C(3)$.
The hypercharge operator $\hat{Y}$ gives the eigenvalue of the hypercharge of the field it is applied to (see table \ref{tab:SMfieldcontent}). $\vec{\tau}$ and $T^a$ are the geneators of $SU_L(2)$ and $SU_C(3)$ respectively. In the fundamental representation $\vec{\tau} = \frac{\vec{\sigma}}{2}$ where $\vec{\sigma}$ has the 3 Pauli matrices as components and $T^a = \frac{\lambda^a}{2}$ where $\lambda^a$ are the 8 Gell-Mann matrices. $\varepsilon_{abc}$ and $f_{abc}$ are the structure constants of $SU_L(2)$ and $SU_C(3)$ respectively.}\label{tab:SM_transformations}

@@

%\begin{table}[H]
%\begin{center}
%\begin{tabular}{|c|l|}
%\hline
% & $U(x) = \mathrm{exp}\left(-ig_Y\frac{\hat{Y}}{2}\theta_Y(x)\right)$\\
% $U_Y(1)$ & $\psi(x) \to \left( 1 - ig_Y\frac{\hat{Y}}{2}\theta_Y(x)\right)\psi(x)$\\
% & $B^\mu(x) \to B^\mu(x) + \partial^\mu\theta_Y(x)$\\
%\hline
% & $U(x) = \mathrm{exp}\left(-ig_w \vec{\tau} \cdot \vec{\theta}_w(x)\right)$\\
% $SU_L(2)$ & $\psi(x) \to \left( \mathbbm{1} - ig_w \vec{\tau} \cdot \vec{\theta}_w(x)\right)\psi(x)$\\
% & $W^{a\mu}(x) \to W^{a\mu}(x) +\partial^\mu\theta^a_w(x) + g_w \varepsilon^{abc} \theta^b_w(x)W^{c\mu}(x)$\\
%  \hline
% & $U(x) = \mathrm{exp}\left(-ig_s T^a \cdot \theta_s^a(x)\right)$\\
%$SU_C(3)$ & $\psi(x) \to \left(\mathbbm{1}-ig_s T^a \cdot \theta_s^a(x)\right)$\\
% & $G^{a\mu}(x) \to G^{a\mu}(x) + \partial^\mu\theta^a_s(x) + g_s f_{abc} \theta^b_s(x)G^{c\mu}$\\
% \hline
%\end{tabular}
%\caption{The table lists the explicit element $U(x)$ of the gauge groups $U_Y(1)$, $SU_L(2)$ and $SU_C(3)$ and the infinitesimal transformations of spinor and vector fields.\newline
%The hypercharge operator $\hat{Y}$ gives the eigenvalue of the hypercharge of the field it is applied to. $\vec{\tau}$ and $T^a$ are the geneators of $SU_L(2)$ and $SU_C(3)$ respectively. In the fundamental representation one has $\vec{\tau} = \frac{\vec{\sigma}}{2}$ where $\vec{\sigma}$ has the 3 Pauli matrices as components and $T^a = \frac{\lambda^a}{2}$ where $\lambda^a$ are the 8 Gell-Mann matrices. $\varepsilon_{abc}$ and $f_{abc}$ are the structure constants of $SU_L(2)$ and $SU_C(3)$ respectively.}\label{tab:SM_transformations}
%\end{center}
%\end{table}

@@

@@

Furthermore the left handed component of quarks interact weakly, which means that their spinors\footnote{The left handed part of a 4-spinor $\Psi$ is projected out by the appropriate projector $P_L$. This is explained in Appendix \ref{sec:2spinor_notation}.} transform (in the fundamental representation) under $SU_L(2)$ transformations meaning that 2 left handed quark spinors are assembled within a doublet.\\
Finally all quarks carry a hypercharge. In section \ref{sec:EWSB} the mechanism of electroweak symmetry breaking is described. This mechanism explains how electromagnetism arises from the groups $SU_L(2)$ and $U_Y(1)$. All quarks interact electromagnetically.\\
After all there are 6 quarks which are listed in table \ref{tab:generations}. They are categorized in 3 generations because their quantum numbers except for their masses reoccur in each generation. The two types of quarks within a generation which have distinct quantum numbers are referred to as up-type and down-type quarks. An up-type-quark and the down-type quark of the same generation built up a doublet.

@@

@@

Quarks and Leptons are the matter particles of the Standard Model. They are listed together with their charges for the different forces in table \ref{tab:SMfieldcontent}. There is the color for strong interactions, the third component of the weak isospin $I_3$ for weak interactions (the eigenvalue of the third generator of the $SU_L(2)$) and the half of the hypercharge $\frac{Y}{2}$ to obtain the electric charge $Q$ via the Gell-Mann–Nishijima formula: $Q = I_3 + \frac{Y}{2}$.\\
Because the left and right-handed parts of spinors transform differently under the $SU_L(2)$ they are listed separately. All quarks occur with three different colors.\\

@@

\caption{This table lists all matter particles in the Standard Model and the Higgs particle with their charges for all forces. This is the color, the weak isospin $I_3$, the half of their hypercharge and their electrical charge. The index $i = 1,2,3$ labels the generation of the matter particles and is written out in table \ref{tab:generations}. If there are no colors specified or charges are zero this means that the fields in question transform trivially under the pertaining gauge transformation.}\label{tab:SMfieldcontent}

@@

\subsubsection*{The Force Particles}
\begin{table}[H]
\begin{center}
\begin{tabular}{c|c|c?c|c|c}
\multicolumn{3}{c?}{before EWSB} & \multicolumn{3}{c}{after EWSB}\\
\hlinewd{2pt}
group & coupling constant & gauge field & coupling constant & gauge field & Particle\\
\hlinewd{2pt}
$SU_C(3)$ & $g_s$ & $G^a_\mu$ & $g_s$ & $G^a_\mu$ & Gluon\\
$SU_L(2)$ & $g_w$ & $W^b_\mu$ & $g_W = \sqrt{2}g_w$,  &  $W^\pm_\mu$,  & $W^\pm$,  \\
 & & & $g_Z = \sqrt{g_w^2 + g_Y^2}$ & $Z^0_\mu$ & $Z^0$ Boson\\
$U_Y(1)$ & $g_Y$ & $B_\mu$ & $e = g_Y\cdot c_w$ & $A_\mu$ & Photon
\end{tabular}
\caption{The gauge fields and their coupling constants before and after electro weak symmetry breaking (EWSB). The Gluon field is not affected by EWSB. $a = 1,\hdots 8$ and $b=1,2,3$ label the number of gauge fields. $c_w$ is the cosine of the electroweak mixing angle defined in \ref{sec:EWSB}}\label{tab:force_particles}
\end{center}
\end{table}
The force particles are described by gauge fields. The gauge field of $SU_C(3)$ is the gluon field. Because the $SU_C(3)$ has 8 generators there are 8 gluons. Their coupling constant is denoted with $g_s$.\\
For the other force particles in the Standard Model - the $W^\pm$ bosons, the $Z_0$ boson and the photon the situation is slightly more involved. They are obtained as a mixture of the $W^b_\mu$ ($b=1,2,3$) and the $B_\mu$ field which are the gauge fields of $SU_L(2)$ and $U_Y(1)$ respectively. This mixing procedure is explained in section \ref{sec:EWSB}.\\
For the moment being the coupling constants and gauge fields before and after this mixing are quoted in table \ref{tab:force_particles}.\bigbreak
The Lagrangian of the SM is built up by qualitatively different terms. Firstly there are the kinetic and minimal coupling terms of the matter fields 
\begin{align}
\mathcal{L}_{\mathrm{matter}} =  \sum_{i=1}^3 \left( \overline{\ell}_{iL} i \slashed{D} l_{iL} + \overline{e}_{iR} i \slashed{D} e_{iR} + \overline{q}_{iL} i \slashed{D} q_{iL} + \overline{u}_{iR} i \slashed{D} u_{iR} \right)
\end{align}
where $i \in \left\{1,2,3\right\}$ labels the generations of matter. The gauge covariant derivative is given by
\begin{align}
D_\mu = \partial_\mu + i g_Y\frac{\hat{Y}}{2} +ig_w \vec{\tau}\cdot \vec{W}^\mu + i g_s T^a G_a^\mu
\end{align}
where for each field the corresponding representation (fundamental or trivial) of the gauge group is to be inserted (see table \ref{tab:SMfieldcontent}). The hyper charge operator $\hat{Y}$ gives the eigenvalue of the hypercharge of the field it is applied to. These can also be found in table \ref{tab:SMfieldcontent}.
The kinetic terms of the gauge fields are given by
\begin{align}
\mathcal{L}_{gauge} = -\frac{1}{4}F^{\mu\nu}F_{\mu\nu} - \frac{1}{4}W^{a\mu\nu}W^a_{\mu\nu} - \frac{1}{4}G^{a\mu\nu}G^a_{\mu\nu}.
\end{align}
